Queue Aware Precoder Design for Space Frequency Resource Allocation

### 2014-07-02 Report/sub_channel_wsrm.tex
Updated on 16.47:Jul-2

In this method, titled as \acf{QM} \ac{SRA} scheme, we limit the resource allocation over the spatial dimension only by performing \ac{JSFRA} design over each sub-channel in an instant. This scheme can be considered in a system employing the \ac{FFR} like power restrictions on certain sub-channels. It can also be used to reduce the problem dimension by limiting the allocation over the spatial dimension only. It is well suited for the persistent scheduling like schemes, where certain sub-channels are dedicated to only certain users. Imposing the user restrictions in the \ac{JSFRA} scheme adds a non-convex constraint which will be difficult to solve.

For a scheduling slot, the precoders are designed over each sub-channel in a sequential manner with the corresponding user queues are updated with the total transmission allocations made in the previous sub-channels on the same slot.

The queue update is common for \ac{SRA} and band-wise \ac{Q-WSRM} schemes, and the queue length controls the design of precoders for the allocation of spatial resources for each sub-channel. The queues are updated before designing the precoders for each sub-channel \me{n} as
\begin{equation}
Q_{k,n} = \max{\Big \lbrace Q_k - \sum_{j = 1}^{n-1} \, \sum_{l = 1}^{L} \, t_{l,k,j} ,0 \Big \rbrace }, \; \forall \; k \in \mathcal{U}
\label{eqn-weight}
\end{equation}
where \me{Q_k} is given by \eqref{eqn-2a} for the user \me{k}. The weight for the sub-channel \me{n} is given by \eqref{eqn-weight}, which uses the allotted transmission bits \me{t_{l,k,j}} evaluated from the earlier sub-channels \me{j < n}. The \ac{QM} \ac{SRA} scheme depends on the permutation pattern of the sub-channel selection order for the precoder design and the performance.

>>>>

The complexity involved in the \ac{JSFRA} scheme scales up significantly based on the sub-channel over which the decision has to be made. Not only the complexity, but also the convergence speed depends on the size  and the number of decision variables involved in the optimization problem. In order to reduce the complexity involved in the \ac{JSFRA} scheme, we provide an alternative sub-optimal solution, where the precoders are designed over each sub-channel independently in a sequential manner by taking the remaining number of queued bits into consideration. It provides an alternative way to the parallel sub-channel wise precoder update using the decomposition techniques discussed in \cite{palomar2006tutorial,boyd2011distributed}.

The proposed \acf{QM} \ac{SRA} scheme decouples the fixing the power across each sub-channel to a constant value as compared to the global power constraint defined by \eqref{eqn-4.3}. In contrast to the decomposition based approach for sub-channel wise resource allocation, this method requires the update on the number of queued bits before each sub-channel level optimization. In this approach, the number of queued bits are updated by the difference between the total number of queued bits during the current slot and the total number of bits that are guaranteed by the earlier sub-channel wise allocations in the same slot as
\begin{equation}
Q_{k,n} = \max{\Big \lbrace Q_k - \sum_{j = 1}^{n-1} \, \sum_{l = 1}^{L} \, t_{l,k,j} ,0 \Big \rbrace }, \; \forall \; k \in \mathcal{U}
\label{eqn-weight}
\end{equation}
where \me{Q_{k,n}} is the total number of queued bits used in the optimization problem carried out for the sub-channel \me{n}. In the expression \eqref{eqn-weight}, \me{Q_k} denotes the total number of queued bits waiting to be transmitted for the user \me{k} during the current slot and \me{t_{l,k,j}} is the rate or guaranteed bits allocated over the sub-channel \me{j}. The current scheme is very sensitive to the order in which the sub-channels are selected for the optimization problem.
